%% LaTeX2e class for student theses
%% sections/content.tex
%% 
%% Karlsruhe Institute of Technology
%% Institute for Program Structures and Data Organization
%% Chair for Software Design and Quality (SDQ)
%%
%% Dr.-Ing. Erik Burger
%% burger@kit.edu
%%
%% Version 1.2, 2016-09-20

\chapter{Acknowledgements}
\label{ch:ack}

%% -------------------
%% | Example content |
%% -------------------

I would like to thank professor Koos for allowing me to work in the institute. Thanks to Muhammad Billah and Yasar Kutuvantavida for allowing me to work with them for the past seven months. I know it was difficult, but we made it through.

Additional acknowledgments must be given to other members of IPQ that helped throughout the whole process: To Juned Kemal for the support on the systems side to perform the data transmission experiments, we would have not reached above half-a-terabit data rates without your help. Thanks to Matthias Blaicher, Heiner Zwickel and Tobias Hoose for the feedback during the reviews of the presentations. 

Finally, thanks to my colleagues Rastko and Anirudh for the emotional support, much required at times when things just plain did not go anywhere. To my parents and sister who probably don't understand what I am doing, but still they know I am doing something, somewhere, to be proud of, for reasons that are difficult to grasp too. But they know I am fine and still breathing. This is for the hearts still beating.
%It has been a long six months. Nearly eight, considering all the downtime before I actually started, and then a lot of trial and error. And trying, and making mistakes, and then that a little bit more.

%This is my acknowledgement of everything that made me miserable, sad, angry, frustrated, and every once in a while, content with the fact that I will die alone and the universe is a meaningless, absolutely random steaming pile of entropic shit.

%First, I would like to say to all those dancing test needles to go fuck themselves, I must have scratched all my pads because of your god-damned motherfucking fault and I hate you for that. I would like to tell the LDX-3412 ILX Lightwave precision current source (TM) to fo fuck itself too, I could have saved precious hours if I had known before that poor contact to a micro-pad could lead to current consumption but not directly to light emission (who knew, right?). I would also like to tell the integrating sphere to go fuck itself as well, I can't believe there is not a more compact model as of today that does not push everything on its way and scratches the micro-pads as a nice ``fuck you, Orlando, you don't deserve to be happy with your results ever''. I would also like to acknowledge that 

%And Anirudh Venkata Pammi, I acknowledge you exist. You piece of trash, useless garbage human.
%% ---------------------
%% | / Example content |
%% ---------------------